### 2021-10-05 plos_latex_template.tex
added marks2021 reference on conferences, diversity & disability to .bib and suggested places for it in .tex
Updates from Overleaf

\section{Express the welcoming spirit in your communication strategy}
\label{rule_communication}
%ast: sara mentioned something that can be good spirit for the communication rule: don't do anything to the outside that you are not doing for your team. it's communication strategy but also there should be coherence between your actions and your words. %Rocío: I love that. Please add it.

\begin{itemize}
    \item Promotion: Actively reach out and promote the conference to people who have been systematically excluded/Outreach/promotion plan that reaches communities that are traditionally excluded in scientific meetings
    \item Include explicit descriptions of accessibility and other inclusion practices in your communication strategy. Help people answer the question "Can I attend this conference?" without the emotional labor of contacting the organizers.
    \item Express this welcoming spirit in your communication strategy: Be public about your commitment to equity and inclusion: display the CoC prominently in conference spaces, publish the diversity statement, fee waivers, abstract selection process
    \item Languages
    \item Words matter: Be careful how you talk about minoritized people, Assertively set tone of inclusion
    \item coherence between actions and words
    \item \textbf{networking} when you gather a diverse groups of attendants you also have to take care of the spaces where they will interact
\end{itemize}

>>>>

\section{Express the welcoming spirit in your communication strategy}
\label{rule_communication}
%ast: sara mentioned something that can be good spirit for the communication rule: don't do anything to the outside that you are not doing for your team. it's communication strategy but also there should be coherence between your actions and your words. %Rocío: I love that. Please add it.
An inclusive communication is to give each individual within the conference a voice and sense of belonging. Embedding inclusion in your communication strategy can only come by design, it shouldn’t be a thoughtless default. In the essense of your communication strategy, you should pritorise and attend to the needs of your team, in other words, don't do anything to the outside that you are not doing for your team. As you plan the conference, actively reach out and promote the conference to people who have been systematically excluded. Design a promotion plan that reaches communities that are traditionally excluded in scientific meetings. This could be by including representatives from these communities in the organising team.Always  include explicit descriptions of accessibility and other inclusion practices. Help people answer the question "Can I attend this conference?" without the emotional labor of contacting the organizers.

\begin{itemize}
    \item Express this welcoming spirit in your communication strategy: Be public about your commitment to equity and inclusion: display the CoC prominently in conference spaces, publish the diversity statement, fee waivers, abstract selection process
    \item Languages
    \item Words matter: Be careful how you talk about minoritized people, Assertively set tone of inclusion
    \item coherence between actions and words
    \item \textbf{networking} when you gather a diverse groups of attendants you also have to take care of the spaces where they will interact
\end{itemize}
